\SW Collaboration Publication Policy: CFHT-LS

### 2014-05-14 doc/sw-publication-policy-cfhtls.tex
Further edtis on CFHT-LS policy

\begin{itemize}
\item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
\item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates. 
\item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
\item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
\item \sw X: New lenses(s) in \sw (authored by collaboration members)
\end{itemize}

There maybe further series papers (TBC).\newline

\subsection{\sw Related Papers}
These are \sw related papers but do not necessarily fall into the \sw paper series
\begin{itemize}
\item Lens modelling in \sw (Spaghetti Lens)
\item New lenses(s) in \sw (authored by persons not part of the \sw collaboration)
\end{itemize}

Please email the \sw PIs at spacewarpspi@googlegroups.com if you have any ideas for further \sw series papers (this includes any publications that include a new lens system that was found by \sw). The authorship policy is defined in the next section.

@@

\subsection{Journal Papers}
\label{sec:series}
A core team of collaborators will participate in writing journal papers, and many collaborators who have made a \textit{significant contribution} to \sw will be recognised on the author
lists of journal papers presenting \sw results.  However, not all collaboration members will participate in writing journal papers.  \textit{Significant contributions} include those who have contributed to:
\begin{itemize}
\item the site design, construction and operation
\item data preparation or analysis
\item writing and editing the papers. 
\end{itemize}

@@

\noindent The author categories are grouped according to collaboration membership (defined above). These authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names.

The Principal Investigators, Zooniverse development team and \sw Science team all have ``opt-out'' status and the \sw Affiliates have ``opt-in'' status.

@@

For \sw related papers, the \sw PIs should be contacted for a suggested minimum contingent of collaboration authors to be added to the paper. These papers are treated with the same status as the general \sw Please also refer to the general \sw policy document

@@

\appendix
\section{Current Author List for \sw series papers: author.tex}
\label{sec:appa}
{\small \verbatiminput{authors.tex}}

>>>>

\begin{itemize}
% Old versions of this list, which caused a conflict when I (PJM) merged in
% Aprajita's May 2014 edits. Both look out of date to me! Suggested new 
% version is beneath these.
% 
% <<<<<<< HEAD
% \item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
% \item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates. 
% \item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
% \item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
% \item \sw X: New lenses(s) in \sw (authored by collaboration members)
%
% =======
% \item \sw I: The system paper, describing the project, the interface, the
% classification analysis methods (SWAP) and results 
% \item \sw II: The \sw  simulations and community performance (not selection
% function), means by which you can compute a selection function for any given
% analysis. 
% \item \sw III: The first new candidates from CFHT-LS \textit{including models,
% follow-up if feasible}
% \item \sw IV: The results from CFHT-LS search including the comparison and
% analysis of citizen scientist classification versus lens-finding algorithms
% (maybe split into smaller papers).
% >>>>>>> 34d2fe73486cc68b301665b1b811cff7804137e8
%
\item \sw I: The system paper, describing the project, the interface & training scheme, the classification analysis methods (SWAP) and results from classification of the training set. (Marshall et al.)
\item \sw II: The \sw CFHTLS project, including description of CFHT-LS specific information (e.g. data/subjects, generation of simulated images), results new lens candidates, and preliminary analysis of \sw compared to previous semi-automatic lens searches in this survey. (More et al.)
\item \sw III: Detailed comparison and analysis of citizen scientist classification versus lens-finding. (More et al.)
%AV to PJM: i thought Anu still wanted the sim-automated serach comparison to be considered in a separate paper
\item \sw IV-X: Detailed results on candidates from CFHT-LS \textit{inclduing lens models, follow-up etc.} (IV: Verma et al. & authored by collaboration members)
\end{itemize}

There maybe further papers written in this series. \newline

\subsection{\sw Related Papers}
These are \sw related papers but do not necessarily fall into the \sw paper series. Planned examples are:
\begin{itemize}
\item Lens modelling in \sw with {\sc Spaghetti Lens})
\item New lenses(s) in \sw (authored by persons not part of the \sw collaboration)
\end{itemize}

% PJM: not sure if this section should be here, it was part of a conflict I 
% got when I merged... Aprajita?
% AV: It was supposed to be here, is a procedure for collaborators to suggest papers

Please email the \sw PIs at \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com} if you have any
ideas for further \sw series or related papers.

@@

The authorship policy for \sw series and related papers is defined here.

\subsection{Journal Papers}
\label{sec:series}

A core team of collaborators will participate in writing journal papers, and
many collaborators who have made a \textit{significant contribution} to \sw
will be recognised on the author lists of journal papers presenting \sw
results.  However, not all collaboration members will participate in writing
journal papers.  \textit{Significant contributions} include those who have
contributed to:
\begin{itemize}
\item the site design, construction and operation
\item data preparation or analysis
\item writing and editing the papers. 
\end{itemize}

@@

\noindent The author categories are grouped according to collaboration membership (defined above). These authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names based on what they have contributed.

For the CFHT-LS \sw system papers, the Principal Investigators, Zooniverse development team and \sw Science team all have ``opt-out'' status and the \sw Affiliates have ``opt-in'' status.

@@

For \sw related papers, the \sw PIs should be contacted via \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com} for a suggested minimum contingent of collaboration authors to be added to the paper, consistent with the policy for general/future \sw projects (please see Guidelines and Policy for Surveys using \sw in this directory).

@@

\appendix
\section{Current Author List for \sw series papers:}
\label{sec:appa}
{\small \verbatiminput{authors.tex}}
